plackett_luce_monster

### 2022-07-09 inst/plackett_luce_monster.Rmd
nice profile likelihood graph

```{r,label=calculateoxcam,cache=TRUE}
maxp(H3(oxcam=1.8888),give=TRUE,n=6)$likes
```

>>>>

```{r,label=calculateoxcam,cache=TRUE}
o <- function(oxcam){maxp(H3(oxcam),give=TRUE,n=1)$likes}
oc <- exp(seq(from=log(0.5),to=log(5),len=15))
L <- sapply(oc,o)
L <- L - max(L)
```

```{r,label=plotoxcam}
plot(log(oc),L,type="b")
abline(v=0)
```
